\texttt{timeline} Documentation

### 2016-06-10 docs/documentation/documentation.tex
added some additional documentation

This section contains a description of all used external dependencies (e.g. libraries) and why they were used in this project.
The python dependencies can be installed using \texttt{pip}, the Python package manager, using the \texttt{requirements.txt} file. 
It is recommended to use a virtual environments when developing for this project to avoid conflicts with other system-wide installed versions of the same dependencies.

@@

\begin{description}
 \item[jQuery]
 \item[MetricsGraphics.js]
 \item[Bootstrap]
\end{description}

>>>>

This section contains a description of all used external dependencies (e.g. libraries) and why they were used in this project.
The python dependencies can be installed using \texttt{pip}, the Python package manager, using the \texttt{requirements.txt} file. 
It is recommended to use a virtual environment when developing for this project to avoid conflicts with other system-wide installed versions of the same dependencies.

@@

\begin{description}
 \item[jQuery] jQuery is the feature rich JavaScript library to simplify client-side scripting. 
 In this project it is mainly used for AJAX calls.
 \item[MetricsGraphics.js] MetricsGraphics.js is used to render the time series visualizations.
 It is based on the well-known D3.js graphic library and provides all necessary primitives and features to plot the required figures.
 \item[Bootstrap] This CSS framework is used to for its beautiful design templates to provide a familiar and responsive user interface.
 Furthermore, some bootstrap add-ons were used for additional widgets (e.g. the bootstrap datetime picker).
\end{description}
